---
title: "KNNForMissingValues"
output: html_document
---

## The data is wns_inno data available on kaggle which is the data whether the person gets the promotion or not.
## Data has contained some missing values in the education column and in the previous_year_rating one. Earlier I have shared the code for the same to fill the missing values using the "mice" package as the mice package used the "Multivariate Imputation by Chained Equations"
## Using the KNN which is the K Nearest Neighbor Algorithm to fill the missing values.

## Loading the data and observing the structure of the data

```{r}
HRTrain_Data <- read.csv(file = "HRTrainData.csv", sep = ",", na.strings = "")
str(HRTrain_Data)
```
# Summary of the data

```{r}
summary(HRTrain_Data)
```
# using the package vlm to do the imputation of the missing data using KNN

```{r}
KnnImputation1 <- kNN(HRTrain_Data, variable = c("previous_year_rating","education"), k = 5)
```
# Summary of the data after imputation

```{r}
summary(KnnImputation1)
```
# Na value has been replaced with the predicted ones using the K nearest neighbor algoritm

